---
title: "Reproducible analysis workflow with R"
author: "Cornelius Hennch"
date: '`r format(Sys.Date(), "%d.%m.%Y")`'
output: 
  beamer_presentation:
    theme: "default"
    colortheme: "dove"
    fonttheme: "structurebold"
    dev: cairo_pdf
    latex_engine: "xelatex"
    keep_tex: yes
mainfont: Fira Sans
classoption: "aspectratio=169"
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

How does this get bigger? hello

1. Bullet 1
2. Bullet 2
3. Bullet 3


## Backup slides

Sometimes, it is useful to add slides at the end of your presentation to
refer to during audience questions.

The best way to do this is to include the `appendixnumberbeamer`
package in your preamble and call `\appendix` before your backup slides.

## R Appendix: R Figure Example

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):

```{r pressureCode, eval=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Appendix: R Figure Example
  
```{r pressureFig, echo=FALSE, fig.align='center', out.width='80%'}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Appendix: R Table Example
  
A simple `knitr::kable` example:  

```{r kableEx, echo=FALSE}
knitr::kable(mtcars[1:5, 1:8],
             caption="(Parts of) the mtcars dataset")
```


